---
title: "WebGIS Final Portfolio"
subtitle: "WebGIS Portfolio"
author: "Michelle Marasco"
date: "5/12/2020"
output:
  html_document:
    theme: readable
    toc: TRUE
    toc_float: TRUE
editor_options:
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
options(knitr.duplicate.label = TRUE)
```

<!-- Everything above this line is the header. -->


<!-- The following text won't be displayed in your document.  It tells R how to make nicer looking buttons for your tabbed content. -->

<style type="text/css" rel="stylesheet">

.btn {
    border-width: 0 0 0 0;
    font-weight: normal;
    text-transform: none;
}

.btn-default {
    color: #2ecc71;
    background-color: #ffffff;
    border-color: #ffffff;
}
</style>



# Introduction

This page will serve as both a repository for my WebGIS 2021 portfolio, and a space to reflect 


# Part I: Maps

## Map Production: Michigan Aurora Borealis Photography Sites {.tabset .tabset-pills}

### The Map


```{r, echo=FALSE}
knitr::include_url("https://umass-amherst.maps.arcgis.com/apps/StoryMapBasic/index.html?appid=a04b9d1082514a709011f703811b7271")
```

<iframe src = https://umass-amherst.maps.arcgis.com/apps/StoryMapBasic/index.html?appid=a04b9d1082514a709011f703811b7271></iframe>


### link to webmap

This map is available here: 

https://umass-amherst.maps.arcgis.com/apps/StoryMapBasic/index.html?appid=a04b9d1082514a709011f703811b7271

### input data and methodology

Aurora data from previous MCDA suitability analysis
  




## Map Production: Numerical Data Exploration  {.tabset .tabset-pills}

### Intro

The intention of these to maps was to show how data can be improved upon


### Unedited Input

https://umass-amherst.maps.arcgis.com/apps/View/index.html?appid=dff1ee33634a4518bea1d7b6c131e2b7


### Edited Input
https://umass-amherst.maps.arcgis.com/apps/View/index.html?appid=dff1ee33634a4518bea1d7b6c131e2b7

### Second Edit
.......


## Michigan Brown Trout: a Tool Analysis {.tabset .tabset-pills}

See the final project description for a list of the required functions.

### `map`

https://umass-amherst.maps.arcgis.com/apps/MapSeries/index.html?appid=56938e49636e4e90b8904a485eed2583



### `discussion`

The purpose of this map was to test different tools of ArcGIS Online.


## Google Map {.tabset .tabset-pills}

A Google map made with javascript of a place I like to take day trips to, Saint Joseph, Michigan

### map

### link

### discussion


## Map Box {.tabset .tabset-pills}

### map

### link

### discussion

## Bonus Map! Aurora Borealis Revisited {.tabset .tabset-pills}

I remade the Aurora Borealis sites map using MapBox and a heat map symbology. For fun

### `map`

```{r echo = FALSE, out.width= "100%", out.height= '1000 px'}
knitr::include_url("AuroraRevisited.html")
```

### `link`
This map is also available here:
https://arelativist.github.io/WebGIS/AuroraRevisited.html


### `methodology`

## Bonus Map! VGI Food Map

### map

### link

### discussion


# Part II: Credentials

A classification of my qualifications and certifications


## HTML Resume {.tabset .tabset-pills}

### `Resume 2021`

```{r, echo=FALSE}
knitr::include_app("MMarasco_Resume2021.html")

```


### `link to resume page`

This HTML Resume is Available here:
https://arelativist.github.io/WebGIS/MMarasco_Resume2021.html


### `info`

This HTML Resume was created as a challenge to implement basic HTML skills on a document from scratch.


## Open Street Map and Humanitarian Open Street Map 

### `OSM Profile`

Here is my OSM Profile, where you can see some of my contributions:

https://www.openstreetmap.org/user/arelativist

## ESRI Trainings

### `link`

## Datacamp Trainings

### `link`

## Codecademy Trainings

### `link` 

## Linkedin Profile

Engaging with the GIS Community

### `link`


# Part III: Miscellaneous

## VGI Input Survey

### concept

### link

### results

# <font size = "+1"><i> The End! Thank you! <i></font>

