---
title: "WebGIS Final Portfolio"
subtitle: "WebGIS Portfolio"
author: "Michelle Marasco"
date: "5/12/2020"
output:
  html_document:
    theme: readable
    toc: TRUE
    toc_float: TRUE
editor_options:
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
options(knitr.duplicate.label = TRUE)
```

<!-- Everything above this line is the header. -->


<!-- The following text won't be displayed in your document.  It tells R how to make nicer looking buttons for your tabbed content. -->

<style type="text/css" rel="stylesheet">

.btn {
    border-width: 0 0 0 0;
    font-weight: normal;
    text-transform: none;
}

.btn-default {
    color: #2ecc71;
    background-color: #ffffff;
    border-color: #ffffff;
}
</style>



# Introduction

This page will serve as both a repository for my WebGIS 2021 portfolio, and a space to reflect. </br>
I hope that this compendium serves to demonstrate my fluency in a broad range of platforms. 


# Part I: Maps

## Map Production: Michigan Aurora Borealis Photography Sites {.tabset .tabset-fade}

This map displays potential photography sites as point data by a suitability ranking attribute that was created using a Multi Criteria Decision Analysis (MCDA). The suitability ranking is a comparing sites on their suitability as potential Aurora Borealis Photography locations. As the Aurora can often be seen by a camera's sensor when it remains undetectable to the human eye, predetermined suitable sites are necessary for Aurora photographers.

### The Map


```{r, echo=FALSE, out.width= "100%"}
knitr::include_url("https://umass-amherst.maps.arcgis.com/apps/StoryMapBasic/index.html?appid=a04b9d1082514a709011f703811b7271", height = "600 px")
```

### Link To WebMap

This WebMap is available here: 

https://umass-amherst.maps.arcgis.com/apps/StoryMapBasic/index.html?appid=a04b9d1082514a709011f703811b7271

### Input Data and Methodology

Aurora photography suitability data from previous MCDA suitability analysis.

More information is available here:
https://umass-amherst.maps.arcgis.com/home/item.html?id=2daa35832a394125937132185e2f5797

These data points were selected and ranked using several suitability factors, based upon original input point data from The State of Michigan's GIS Open Data Database (https://gis-michigan.opendata.arcgis.com/)



## Map Production: Morchella Americana Distribution in North America  {.tabset .tabset-fade }

The purpose of this map production was to demonstrate the capabilities of ArcGIS Online in displaying spatial  data in interesting and illuminating ways. Edited and symbolized point data is shown in comparison to raw imported point data downloaded from GBIF (https://www.gbif.org/) 

### Edited Input Map

```{r, echo=FALSE, out.width= "100%"}
knitr::include_url("https://umass-amherst.maps.arcgis.com/apps/instant/interactivelegend/index.html?appid=7068fdd9427848d6aba273e1b586e6c4")
```

The intention of these to maps was to show how data can be improved upon. Here is an example of data edited and symbolized in a meaningful way. </br></br>

<b>Link to WebMap:</b> https://umass-amherst.maps.arcgis.com/apps/instant/interactivelegend/index.html?appid=7068fdd9427848d6aba273e1b586e6c4

### Raw Unedited Input Map

``` {r, echo = FALSE, out.width= "100%"}
knitr::include_url("https://umass-amherst.maps.arcgis.com/apps/instant/minimalist/index.html?appid=401ac97ebfd44ad097512f11a13ec5f6")
```

Here is the map of the raw point data loaded into ArcGIS unedited and unsymbolized.
</br></br>
<b>Link to WebMap: </b> https://umass-amherst.maps.arcgis.com/apps/instant/minimalist/index.html?appid=401ac97ebfd44ad097512f11a13ec5f6

### Second Round Edit
.......
Coming Soon


## Michigan Brown Trout Distribution: A Tool Analysis {.tabset .tabset-fade}

An exploration of different tools available within ArcGIS Online and their capabilities

### The Map
```{r echo=FALSE, out.width= "100%"}
knitr::include_app("https://umass-amherst.maps.arcgis.com/apps/MapSeries/index.html?appid=56938e49636e4e90b8904a485eed2583", height = "600 px")

```


### Link to WebMap
<b>Link:</b> </br></br>
https://umass-amherst.maps.arcgis.com/apps/MapSeries/index.html?appid=56938e49636e4e90b8904a485eed2583



### Input Data and Methodology

The purpose of this map was to test the capabilities of the various tools offered by ArcGIS Online.USing the input point data of Brown Trout observations in the State of Michigan, several analyses of the points' spatial distribution were conducted over various spatial units.


## Google Map: a Map Production of St. Joseph, MI {.tabset .tabset-fade}

A Google Map made from scratch with javascript of a place that is nice to spend the day, Saint Joseph, Michigan


### The Map

```{r echo=FALSE, out.width= "100%"}
knitr::include_url("google_html_map.html", height = "500 px")

```
Here is my simple Google Map of the best spots in St. Joe

### Link to WebMap


<b>Link:</b></br>
https://arelativist.github.io/WebGIS/google_html_map.html

### Discussion

The purpose of this map was to build a simple WebMap in Google Maps with markers in JavaScript from scratch. I found this platform to be quite cumbersome. 


## Map Box: a Map Production of St. Joseph, MI {.tabset .tabset-fade}

Another take on the map of my favorite spots in Saint Joseph, Michigan, This time utilizing the Map Box platform.

### The Map

```{r echo = FALSE, out.width = "100%"}
knitr::include_url("StJoeMap.html", height = "500 px")
```


### Link to WebMap

<b>Link:</b></br>
https://arelativist.github.io/WebGIS/StJoeMap.html

### Discussion

I found the MapBox platform to be much preferable to Google Maps. I really enjoyed the process of working in MapBox comparatively. I find it to be much more intuitive.



## Bonus Map! Aurora Borealis Revisited {.tabset .tabset-fade}

I remade the Aurora Borealis sites map using MapBox and a heat map symbology. For fun

### The Map

```{r echo = FALSE, out.width= "100%"}

knitr::include_url("AuroraRevisited.html", height = "600px")

```

### Link
<b>This map is also available here:</b></br>
https://arelativist.github.io/WebGIS/AuroraRevisited.html


### Input Data and Methodology

This map was created using the same input point data as the "Michigan Aurora Borealis Photograpy Sites" map that was created in ArcGIS Online. This platform did seem a bit more intuitive than ArcGIS Online, as well.

## Bonus Map! VGI Food Map Geocoding Comparison {.tabset .tabset-float}
Raw Volunteered Geographic Information (VGI) was obtained from a web survey. Geocoding services of two different platforms were tested on the data and these maps show the results.

### The Map

```{r echo = FALSE, out.width = "100%"}
knitr::include_url("https://umass-amherst.maps.arcgis.com/apps/MapSeries/index.html?appid=8435469094754cc282366efbb2bd7246", height = "500 px")
```


### Link to WebMap

<b>Link:</b></br>
https://umass-amherst.maps.arcgis.com/apps/MapSeries/index.html?appid=8435469094754cc282366efbb2bd7246


### Input Data and Methodology
The input data for these two WebMap layers was exactly the same. One map used ArcGIS online geocoding, and the other used the geogcoding service available within Google Earth Pro. The Google Earth Pro geocoded points were then imported into ArcGIS online. It was surprising how effective the Google Earth Pro geocoding tool was, especially considering that I did not know it existed before this exploration. It seemed to be much more effective than the Arc Online geocoding.</br>
The input data was obtained from an online form and was imported in a comma separated values text format.



# Part II: Credentials

A classification of my qualifications and certifications


## HTML Resume {.tabset }

### Resume 2021

```{r, echo=FALSE, out.width= "100%"}
knitr::include_app("MMarasco_Resume2021.html")

```


### Link To Web Resume

<b>This HTML Resume is Available here:</b></br>
https://arelativist.github.io/WebGIS/MMarasco_Resume2021.html


### Info

This HTML Resume was created as a challenge to implement basic HTML skills on a document from scratch.


## Open Street Map and Humanitarian Open Street Map 

### OSM Profile

Here is a link to my OSM Profile, where you can see some of my contributions:</br>

https://www.openstreetmap.org/user/arelativist </br>


## ESRI Trainings {.tabset .tabset-fade}
I have completed several training courses online through ESRI, and below is a current transcript of ESRI Training Courses that I have completed:

### Transcript
```{r echo = FALSE, out.width= "100%", out.height= "500 px"}
knitr::include_graphics("Michelle_Marasco_ESRI.pdf")

```
ESRI Courses Transcript
</br>

### Link
<b>Link to PDF of the transcript:</b></br>
https://arelativist.github.io/WebGIS/Michelle_Marasco_ESRI.pdf

## Datacamp Trainings {.tabset .tabset-fade}
I have also complete several training courses through Datacamp.

### Profile

My profile including courses that I have completed is available here:</br>

https://www.datacamp.com/profile/mmarasco


## Codecademy Trainings {.tabset .tabset-fade}

I have studied through Codecademy, as well, and below is a link to my profile with information on courses completed. </br>

### Profile
My Codecademy Training Profile: </br>
https://www.codecademy.com/profiles/gigaNinja20552

## Linkedin Profile {.tabset .tabset-fade}

Engaging with the GIS Community. </br>

### Profile

<script src="https://platform.linkedin.com/badges/js/profile.js" async defer type="text/javascript"></script>
<div class="badge-base LI-profile-badge" data-locale="en_US" data-size="large" data-theme="light" data-type="VERTICAL" data-vanity="michellemarasco" data-version="v1"><a class="badge-base__link LI-simple-link" href="https://www.linkedin.com/in/michellemarasco?trk=profile-badge">Michelle Marasco</a></div>
              
My LinkedIn Profile

### Link

The link to my Public Profile Page:</br>
http://www.linkedin.com/in/michellemarasco

# Part III: Miscellaneous

## VGI Input Survey {.tabset .tabset-float}
This is a demonstration of a way to collect Volunteered Geographic data. In this case it is a sample survey of collecting location data from a field crew.

### Survey
```{r echo=FALSE}
knitr::include_url("https://arcg.is/1aqSOr")

```

### Concept
This survey was created as a demonstration of how to use a survey to collect data. The concept of the survey is that field crews could report their location back and that data could be updated in the database.</br>
<b>Direct Link to the Survey:<b></br>
https://arcg.is/1aqSOr</br>

### Results

</br>
No results yet!
</br>

## <font size = "+3"> <i>The End! Thank you! <i></font>

