---
title: "WebGIS Final Portfolio"
subtitle: "WebGIS Portfolio"
author: "Michelle Marasco"
date: "5/12/2020"
output:
  html_document:
    theme: readable
    toc: TRUE
    toc_float: TRUE
editor_options:
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
options(knitr.duplicate.label = TRUE)
```

<!-- Everything above this line is the header. -->


<!-- The following text won't be displayed in your document.  It tells R how to make nicer looking buttons for your tabbed content. -->

<style type="text/css" rel="stylesheet">

.btn {
    border-width: 0 0 0 0;
    font-weight: normal;
    text-transform: none;
}

.btn-default {
    color: #2ecc71;
    background-color: #ffffff;
    border-color: #ffffff;
}
</style>



# Introduction

This page will serve as both a repository for my WebGIS 2021 portfolio, and a space to reflect 


# Part I: Maps

## Map Production: Michigan Aurora Borealis Photography Sites {.tabset .tabset-fade}

This map displays potential photography sites as point data by a suitability ranking attribute that was created using a Multi Criteria Decision Analysis (MCDA). The suitability ranking is a comparing sites on their suitability as potential Aurora Borealis Photography locations. As the Aurora can often be seen by a camera's sensor when it remains undetectable to the human eye, predetermined suitable sites are necessary for Aurora photographers.

### The Map


```{r, echo=FALSE, out.width= "100%"}
knitr::include_url("https://umass-amherst.maps.arcgis.com/apps/StoryMapBasic/index.html?appid=a04b9d1082514a709011f703811b7271", height = "600 px")
```

### Link To WebMap

This WebMap is available here: 

https://umass-amherst.maps.arcgis.com/apps/StoryMapBasic/index.html?appid=a04b9d1082514a709011f703811b7271

### Input Data and Methodology

Aurora photography suitability data from previous MCDA suitability analysis.

More information is available here:
https://umass-amherst.maps.arcgis.com/home/item.html?id=2daa35832a394125937132185e2f5797

These data points were selected and ranked using several suitability factors, based upon original input point data from The State of Michigan's GIS Open Data Database (https://gis-michigan.opendata.arcgis.com/)



## Map Production: Morchella Americana Distribution in North America  {.tabset .tabset-fade }

The purpose of this map production was to demonstrate the capabilities of ArcGIS Online in displaying spatial  data in interesting and illuminating ways. Edited and symbolized point data is shown in comparison to raw imported point data downloaded from GBIF (https://www.gbif.org/) 

### Edited Input Map

```{r, echo=FALSE, out.width= "100%"}
knitr::include_url("https://umass-amherst.maps.arcgis.com/apps/instant/interactivelegend/index.html?appid=7068fdd9427848d6aba273e1b586e6c4")
```

The intention of these to maps was to show how data can be improved upon. Here is an example of data edited and symbolized in a meaningful way. </br>

Link to WebMap: https://umass-amherst.maps.arcgis.com/apps/instant/interactivelegend/index.html?appid=7068fdd9427848d6aba273e1b586e6c4

### Raw Unedited Input Map

``` {r, echo = FALSE, out.width= "100%"}
knitr::include_url("https://umass-amherst.maps.arcgis.com/apps/View/index.html?appid=dff1ee33634a4518bea1d7b6c131e2b7")
```



### Second Round Edit
.......
Coming Soon


## Michigan Brown Trout Distribution: A Tool Analysis {.tabset .tabset-fade}

See the final project description for a list of the required functions.

### `map`

https://umass-amherst.maps.arcgis.com/apps/MapSeries/index.html?appid=56938e49636e4e90b8904a485eed2583



### `discussion`

The purpose of this map was to test different tools of ArcGIS Online.


## Google Map: a Map Production of St. Joseph, MI {.tabset .tabset-fade}

A Google map made with javascript of a place that is nice to spend the day, Saint Joseph, Michigan

### The Map

### Link to WebMap

### Discussion


## Map Box: a Map Production of St. Joseph, MI {.tabset .tabset-fade}

Another take on the map of my favorite spots in Saint Joseph, Michigan, This time utilizing the Map Box platform.
### The Map

### Link to WebMap

### Discussion

## Bonus Map! Aurora Borealis Revisited {.tabset .tabset-fade}

I remade the Aurora Borealis sites map using MapBox and a heat map symbology. For fun

### map

```{r echo = FALSE, out.width= "100%"}

knitr::include_url("AuroraRevisited.html", height = "600px")

```

### `link`
This map is also available here:
https://arelativist.github.io/WebGIS/AuroraRevisited.html


### `methodology`

## Bonus Map! VGI Food Map Geocoding Comparison

### map

### link

### discussion


# Part II: Credentials

A classification of my qualifications and certifications


## HTML Resume {.tabset }

### `Resume 2021`

```{r, echo=FALSE, out.width= "100%"}
knitr::include_app("MMarasco_Resume2021.html")

```


### `link to resume page`

This HTML Resume is Available here:
https://arelativist.github.io/WebGIS/MMarasco_Resume2021.html


### `info`

This HTML Resume was created as a challenge to implement basic HTML skills on a document from scratch.


## Open Street Map and Humanitarian Open Street Map 

### `OSM Profile`

Here is my OSM Profile, where you can see some of my contributions:
```{r}
knitr::include_app("https://www.openstreetmap.org/user/arelativist/history#map=3/28.71/5.45")
```

https://www.openstreetmap.org/user/arelativist

## ESRI Trainings {.tabset .tabset-fade}
Below is a current transcript of ESRI Trainings I have completed:

### Transcript
```{r echo = FALSE, out.width= "100%", out.height= "500 px"}
knitr::include_graphics("Michelle_Marasco_ESRI.pdf")

```
### Link


## Datacamp Trainings

### Profile
```{r echo= FALSE}

knitr::include_url("https://www.datacamp.com/profile/mmarasco")

```

https://www.datacamp.com/profile/mmarasco


## Codecademy Trainings {.tabset .tabset-fade}

### Profile
My Codecademy Training Profile: </br>
https://www.codecademy.com/profiles/gigaNinja20552

## Linkedin Profile {.tabset .tabset-fade}

Engaging with the GIS Community.

### Profile

<script src="https://platform.linkedin.com/badges/js/profile.js" async defer type="text/javascript"></script>
<div class="badge-base LI-profile-badge" data-locale="en_US" data-size="large" data-theme="light" data-type="VERTICAL" data-vanity="michellemarasco" data-version="v1"><a class="badge-base__link LI-simple-link" href="https://www.linkedin.com/in/michellemarasco?trk=profile-badge">Michelle Marasco</a></div>
              
My LinkedIn Profile

### Link

The link to my Public Profile Page:</br>
http://www.linkedin.com/in/michellemarasco

# Part III: Miscellaneous

## VGI Input Survey

### concept

### link

### results

# <font size = "+1"><i> The End! Thank you! <i></font>

