---
title: "WebGIS Final Portfolio"
subtitle: "WebGIS Portfolio"
author: "Michelle Marasco"
date: "5/12/2020"
output:
  html_document:
    theme: readable
    toc: TRUE
    toc_float: TRUE
editor_options:
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
options(knitr.duplicate.label = TRUE)
```

<!-- Everything above this line is the header. -->


<!-- The following text won't be displayed in your document.  It tells R how to make nicer looking buttons for your tabbed content. -->

<style type="text/css" rel="stylesheet">

.btn {
    border-width: 0 0 0 0;
    font-weight: normal;
    text-transform: none;
}

.btn-default {
    color: #2ecc71;
    background-color: #ffffff;
    border-color: #ffffff;
}
</style>



# Introduction

This page will serve as both a repository for my WebGIS 2021 portfolio, and a space to reflect 


Here is a link to another file:
```{r}
knitr::include_url("http://www.google.com")

```



# Map Production: Michigan Aurora Borealis Photography Sites {.tabset .tabset-pills}

<!-- Look at the source code for the final project template, you'll notice the text: -->
<!-- {.tabset .tabset-pills} -->
<!-- This creates tabbed content for all the following sections that are one-level below. -->
<!-- - If you include them on a primary header (one #), all of the subsequent secondary headers will in tabs. -->




## `The Map`

This map is available here: 

https://umass-amherst.maps.arcgis.com/apps/StoryMapBasic/index.html?appid=a04b9d1082514a709011f703811b7271



## `input data and methodology`

Aurora data from analysis
  




# Map Production: Numerical Data Exploration  {.tabset .tabset-pills}

## Intro

The intention of these to maps was to show how data can be improved upon


## Unedited Input

https://umass-amherst.maps.arcgis.com/apps/View/index.html?appid=dff1ee33634a4518bea1d7b6c131e2b7


## Edited Input
https://umass-amherst.maps.arcgis.com/apps/View/index.html?appid=dff1ee33634a4518bea1d7b6c131e2b7

## Second Edit
.......


# Michigan Brown Trout: a Tool Analysis {.tabset .tabset-pills}

See the final project description for a list of the required functions.

## `map`

https://umass-amherst.maps.arcgis.com/apps/MapSeries/index.html?appid=56938e49636e4e90b8904a485eed2583



## `discussion`

The purpose of this map was to test different tools of ArcGIS Online.


# Map Production: Open Street Map and Humanitarian Open Street Map 

## `OSM Profile`

Here is my OSM Profile, where you can see some of my contributions:

https://www.openstreetmap.org/user/arelativist



# HTML Resume {.tabset .tabset-pills}

## `Resume 2021`

```{r, echo=FALSE}
knitr::include_app("MMarasco_Resume2021.html")

```



## `link to resume page`

link

## `info`

This HTML Resume was created as a challenge to implement basic HTML skills on a document from scratch.

 





# Part 2: Data Anaylsis

Now that it is imported, we will preform a data analysis on the Delomys data.

## Numerical Exploration
We will start with a numerical exploration:

### Summary of `dat_delomys`:

### Shapiro Tests


Since both of these return a p-value that is much lower than .05, we know that our variables are not normally distributed.


## Graphical Exploration {.tabset .tabset-pills}

### Scatterplot



### Histograms


## body length histogram





### Boxplots


## body mass conditioned on species



### Interpretation

1. It appears that body mass and length have a linear relationship. It appears visually that the have a positive linear relationship, with several outliers that have much longer body length.

2. The histograms appear to have a somewhat normal distribution. Body mass histogram appears more normal, and body length, again appears to have several outliers positively.

3. Given the low p-values of the shapiro test for both variables, it seems that they are not normally distributed. Visually, body mass appears to be normally distributed. Length only appears somewhat normally distributed visually. Unconditioned, I would say neither is normally distributed.

4. Based on the conditional boxplots, it appears that D.Dorsalis has a greater body mass, and that the males of both species have a greater body mass as well. The difference in mean body mass between the sexes is greateer in D. Dorsalis, but is present in both species.


## Model Building 

Now we construct the models:

```{r}



```


## Model Diagnostics {.tabset .tabset-pills}

### Visual Diagnostic

Here we use histograms of the residuals as a visual diagnostic:

```{r echo = FALSE}


```

### Numerical Diagnostic

Here we use the Shapiro-Wilk test on the residuals of our models as a numerical diagnostic:

```{r echo = FALSE}

```

### Interpretation

1. Although visually many of the models appear to have a normal distribution, they all return values that demonstrate a violation of the normality assumption under a Shapiro-Wilk normality test.

2. Not all of the models violate the normality assumption with equal severity. While Fit 1, the linear model, appears violate with the most severity, Fit 2, the one way ANOVA based on Sex, appears to have the residuals closest to normality of the models that we have fit.


## Model Interpretation {.tabset .tabset-pills}

### Body Length

#### Model Coefficient Table: Body Length ~ Body Mass


#### Interpretation





### Body Mass: Model Coefficients

#### Model Coefficient Table: Body Mass ~ Sex



#### Model Coefficient Table: Body Mass ~ Species


#### Interpretation

- The base level for sex is female.
- The base level for binomial is D. Dorsalis
- Male is heavier, as you can see by the positive coefficient from the base
- D. Dorsalis is heavier, as you can see by the negative coefficient from the base



### Body Mass: ANOVA

#### ANOVA Table: body_mass ~ sex + binomial




#### Interpretation

- Sex or species alone are not a significant predictor of body mass.
- However, there is a significant interaction between the two.
- The significance differs between the single-predictor, additive, and interactive models. While there appears to be no significance to single-predictor or additive models, the interactive model is significant when both variables are used. While sex or species alone are not significant predictors, taken together as an interaction they are.



## Model Comparison : Body Mass

Finally, we will compare our models using Akaike Information Criterion (AIC)

#### AIC: Model 1

#### AIC: Model 2

#### AIC: Model 3

#### AIC: Model 4

#### AIC: Model 5


#### Interpretation

- Models 2 and 4 have the lowest AIC.
- Though model 2 has a much lower AIC than model 4, in this case I would select model 4, because in this case I think that the added complexity and reduced ease of understanding would be worth the extra insight gained. Also from our previous inquiry, I know that this model creates more significance, and provides more more insight for only a small gain in complexity. 










